Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-29 papers/ms.tex
paper: update ms

\title{
  Three $\approx$40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

Some of the most salient stellar parameters of the KOIs in Cep-Her can
be gleaned by inspecting Figure~\ref{fig:age}.  They span spectral
types of G8V (Kepler-1627) to K8V (KOI-7913 A).  The secondary in the
KOI-7913 system is marginally cooler than the primary.  Since a
Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ million years \citep{choi_mesa_2016}, these
stars are all in the late stages of their pre-main-sequence
contraction.  Their heliocentric distances are $\approx$260\,pc
(KOI-7913 and KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in
RSG-5).

To derive spectroscopic parameters $(T_{\rm eff}, \log g_\star, [{\rm
Fe/H}])$ and to analyze spectroscopic youth proxies such as the
Li\,\textsc{I} 6708\,\AA\ doublet equivalent width and H$\alpha$
emission, we acquired spectra.  The system-by-system details follow.
The results are summarized in Table~\ref{tab:sysparams}.

%\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
%spectrum from Keck/HIRES on the night of 2021 March 26 using the
%standard setup and reduction techniques of the California Planet
%Survey \citep{howard_cps_2010}.  Following the equivalent width
%measurement procedure described by \citet{bouma_2021_ngc2516}, we find
%${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
%given the stellar effective temperature (Table~\ref{tab:starparams}),
%this measurement is in agreement with expectations for a
%$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
%\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
%equivalent widths measured by \citet{berger_identifying_2018} in their
%analysis of 1{,}301 Kepler-star spectra.
%
%
%% rotation period from plot_rotation_period_windowslider.py
%Based on the spatial and kinematic association of \sn\ with the \cn,
%and the assumption that the planet formed shortly after the star, it
%seems likely that \sn\ is the same age as the cluster. There are two
%consistency checks on whether this is true: rotation and lithium.
%Based on the Kepler light curve, the rotation period is
%$2.642\pm0.042$\,days, where the quoted uncertainty is based on the
%scatter in rotation periods measured from each individual Kepler
%quarter.  This is consistent with comparable cluster members
%(Figure~\ref{fig:age}).

%\subsection{Kepler\,1627A}

@@

For Kepler-1643,
we acquired an iodine-free spectrum from Keck/HIRES
...
%FIMXE TODO TODO TODO WORDS LET'S GO!

spectra  (YYYY/MM/DD) and KOI-7913 (YYYY/MM/DD and
YYYY/MM/DD), where for the latter the two different epochs
corresponded to observations of the secondary and primary
respectively.  The acquisition and analysis followed the standard
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  For KOI-7368, we acquired TRES spectra on
YYYY/MM/DD and YYYY/MM/DD.  CITE METHOD PAPER.

\subsection{KOI-7368}
\subsection{KOI-7913}
Is a binary.
The latter system is 3$\farcs$501 
%FIXME FIXME FIXME TODO TODO TODO

@@

%\appendix
%\section{Young, Age-Dated, and Age-Dateable Star Compilation}
%\label{app:targetlist}

>>>>

\title{
  Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia
}

@@

Some salient stellar parameters of the KOIs in Cep-Her can be gleaned
by inspecting Figure~\ref{fig:age}.  They span spectral types of G8V
(Kepler-1627) to K8V (KOI-7913 A).  The secondary in the KOI-7913
system is only marginally cooler than the primary.  And since a
Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ million years \citep{choi_mesa_2016}, these
stars are all in the late stages of their pre-main-sequence
contraction.  Their heliocentric distances are $\approx$260\,pc
(KOI-7913 and KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in
RSG-5).

The adopted stellar parameters are listed in
Table~\ref{tab:starparams}.  The stellar surface gravity, radius,
mass, and density are found by interpolating against the MIST
isochrones \citep{choi_mesa_2016}.  The statistical uncertainties from
this technique mostly originate from the parallax uncertaintes; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

To verify these parameters and to also analyze spectroscopic youth
proxies such as the Li\,\textsc{I} 6708\,\AA\ doublet and H$\alpha$,
we acquired spectra.  We also acquired high resolution imaging for
each system, to constrain the existence of visual companions,
including possible bound binaries.  The system-by-system details
follow, and the the relevant results are also summarized in
Table~\ref{tab:sysparams}.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 August 16 and 2021 October 25.  The acquisition
and analysis followed the standard reduction techniques of the
California Planet Survey \citep{howard_cps_2010}.  We derived the
stellar spectral parameters ($T_{\rm eff}, \log g, R_\star$) using
\texttt{SpecMatch-Emp} \citep{yee_SM_2017}, which yielded values in
$<1$-$\sigma$ agreement with those from the cluster-isochrone
approach.  This approach also yielded $[Fe/H]=0.13 \pm 0.09$.  Using
the broadened synthetic templates from \texttt{SpecMatch-Synth}
\citep{petigura_cksi_2017}, we found $v\sin i = 9.3 \pm 1.0\,\mkms$.
The systemic radial velocity at the two sequence epochs was $-9.1 \pm
1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$ respectively.  To infer the
equivalent width of the Li\,\textsc{I} 6708\,\AA\ doublet, we followed
the procedure described by \citet{bouma_2021_ngc2516}.  This yielded a
strong detection: ${\rm EW}_{\rm Li} = 126^{+8}_{-4}$\,m\AA, with
values consistent at $<1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the Fe\,\textsc{I} blend at
6707.44\AA.

{\bf TODO verify continuum normalization}
Given the reddening-corrected color of the star this is
consistent(ish) with the Pleiades/NGC2516 based on my NGC2516 figure.
But it looks sub-IC2602 based on the lithium.png figure, which uses
the Randich2018 values.
It's pretty clearly super-field.
I really need to verify the continuum normalization.
COMPARE vs:
\citealt{randich_gaiaeso_2018}).  
\citet{berger_identifying_2018}

\paragraph{High-Resolution Imaging}
%FIXME TODO LEFT OFF HERE -- DESCRIBE!

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired TRES spectra on 2015 June 1.  The stellar
parameter classification pipeline for these spectra is described by
\citet{2021tsc2.confE.124B}, and is based on the template library
originally constructed by \citet{buchhave_hatp16b_class_2010}.

%FIXME TODO LEFT OFF HERE -- DESCRIBE!
vsini?  Fe/H?  Li EW?

\paragraph{High-Resolution Imaging}

\subsection{KOI-7913}

\paragraph{Spectra}

KOI-7913 (YYYY/MM/DD and YYYY/MM/DD), where for the latter the two
different epochs corresponded to observations of the secondary and
primary respectively.

\paragraph{High-Resolution Imaging}
Is a binary.
The latter system is 3$\farcs$501 
%FIXME FIXME FIXME TODO TODO TODO

@@

\appendix
\section{Table of Candidate RSG-5 and CH-2 Members}
\label{app:members}

Gaia source lists and abbreviated info.  Include rotation periods.

\section{Table of Transit Fit Parameters}
\label{app:transit}

Table goes here
